\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage[dvipsnames]{xcolor}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
\usepackage{CormorantGaramond}
\usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.4in}
\addtolength{\evensidemargin}{-0.4in}
\addtolength{\textwidth}{0.8in}
\addtolength{\topmargin}{-0.4in}
\addtolength{\textheight}{1.5in}

\urlstyle{same}

\raggedbottom{}
\raggedright{}
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\color{Blue}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{Blue}\titlerule{} \vspace{-2pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1


%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
  {\Huge \scshape Siwakorn Kamondilok} \\ \vspace{5pt}
  \small \raisebox{-0.1\height}\faPhone\ +66 83-953-6059~ \href{mailto:siwakorn.kamo@ku.th}{\raisebox{-0.2\height}\faEnvelope\  \underline{siwakorn.kamo@ku.th}} ~

  \vspace{2pt}
  \href{https://www.linkedin.com/in/swkrn/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/swkrn}}  ~
  \href{https://github.com/swkrn}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/swkrn}}
  \vspace{-8pt}
\end{center}

\vspace{-5pt}



%-----------SUMMARY-------------
\section{Summary}
Passionate and skilled Computer Engineering graduate with a strong interest in software development, 
specializing in App Development, Fullstack Development, and Software Engineering. Eager to leverage my academic background, 
practical experience, and technical abilities to drive innovation and success in collaborative environments.



%-----------PROGRAMMING SKILLS-----------
\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \item{
        \textbf{Languages}{: Python, Kotlin, C++, C\#, JavaScript, Golang, Dart, Swift} \\
        \textbf{Backend}{: Node.js, Express.js, FastAPI, Gin}\\
        \textbf{Frontend}{: React, HTML, CSS, Bootstrap} \\
        \textbf{Clouds \& Databases}{: AWS, Cloudflare, PostgreSQL, MongoDB} \\
        \textbf{Web Technologies}{: Docker, Socket.IO} \\
        \textbf{Developer Tools}{: Android Studio, Xcode, Unity, VS Code, GitHub} \\
        \textbf{Soft Skills}{: Problem Solving, Time Management, Teamwork} \\
        }
\end{itemize}
\vspace{-10pt}



% -----------EXPERIENCE-----------
\section{Work Experience}
\resumeSubHeadingListStart

\resumeSubheading
{TISCO Financial Group}{Apr 2023~-~Jun 2023}
{DevOps Engineer Intern}{On-site}

\vspace{-3pt}

\resumeItemListStart

\resumeItem{Collaborate with a team of software developers and operations professionals.}
\resumeItem{Learn about automation tools and techniques to streamline software development processes.}
\resumeItem{Assist in setting up and maintaining infrastructure, including servers and databases.}

\resumeItemListEnd

\resumeSubHeadingListEnd



%-----------PROJECTS-----------
\section{Projects}
\vspace{-5pt}
\resumeSubHeadingListStart

\resumeProjectHeading{\textbf{XMS}}{}
\resumeItemListStart
\resumeItem{XMS is a real-time chat messaging application designed to provide users with 
a seamless communication experience. It facilitates instant messaging between users in real-time, 
with chat history, allowing for quick and efficient communication.}
\resumeItem{\textbf{Technologies:} Flutter, Express, MongoDB, Socket.IO}
\resumeItemListEnd
\vspace{-13pt}

\resumeProjectHeading{\textbf{POS-ME}}{}
\resumeItemListStart
\resumeItem{POS-ME is a point-of-sale system for merchants who want to save on the cost of renting or buying
a full point-of-sale system. There is a product management system, a billing system that can scan
product barcodes. Payment via PromptPay QR and a sales report system.}
\resumeItem{\textbf{Technologies:} React, Express, MongoDB}
\resumeItemListEnd
\vspace{-13pt}

\resumeProjectHeading{\textbf{Attendance Management System}}{}
\resumeItemListStart
\resumeItem{To limit the number of exhibition participants to prevent the spread of COVID-19 by counting the
number of people in the event and empty seats.\@ and display information on the web in real-time.
This can also manage events, set limits on the number of people, and view the history of events
that have already been organized.}
\resumeItem{\textbf{Technologies:} ESP32, React, FastAPI, MongoDB}
\resumeItemListEnd
\vspace{-13pt}

\resumeProjectHeading{\textbf{Baby Sound Detector}}{}
\resumeItemListStart
\resumeItem{During nighttime or when the child's parents are in another room, 
This device will be able to detect the child's cries and send notifications to the parents' mobile phones via Line, 
enabling them to attend to their child's needs promptly.}
\resumeItem{\textbf{Technologies:} NodeMCU, RaspberryPi, Python}
\resumeItemListEnd
\vspace{-13pt}

\resumeSubHeadingListEnd
\vspace{3pt}



%-----------EDUCATION-----------
\section{Education}

\resumeSubHeadingListStart
\resumeSubheading
{Kasetsart University\textnormal{ -- Bangkok, Thailand}}
{Jul 2020 - Apr 2024}
{Bachelor of Engineering in Computer Engineering. (First Class Honors)}
{3.65/4.0 GPA}
\resumeSubHeadingListEnd

\vspace{-3pt}



\end{document}